Untitled

### 2023-08-16 code/analysis_Redo.Rmd
got it to work!

df.profit <- df.profit %>% 
  left_join(dfc %>% filter(Year == 2010) %>% select(ID, ngla_net_gain_loss, ngla_revenue, ngla_expense, Assets, Pct.NHA:Pct.COM) %>% 
  mutate(profit.class = ifelse(ngla_net_gain_loss / ngla_revenue < 0.017, 1, 
              ifelse(ngla_net_gain_loss / ngla_revenue >= 0.017 & ngla_net_gain_loss / ngla_revenue <= 0.081, 2, 
              ifelse(ngla_net_gain_loss / ngla_revenue > 0.081, 3, NA)))) , by = c("ID"))

@@

  df.temp <- df.profit[,c(1:9, j, 13:ncol(df.profit))] 
  colnames(df.temp)[10] <- "Outcome"
  outcomes <- did2s(
      data = df.temp %>% filter(profit.class == g), 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.MCR + Pct.None, 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "ID",
      verbose = FALSE
    )

@@

  did.profit %>% 
   select(name, `0_0`, `0_1`, `1_0`, `1_1`, Unadjusted, Estimate, `Std. Error`) %>% 
  mutate(Estimate = round(Estimate, 2), 
         `95% CI` = paste(round(Estimate - 1.96 * `Std. Error`, 2), ", ", round(Estimate + 1.96 * `Std. Error`, 2), sep = ""), 
         `% Change` = round(Estimate / `1_0` * 100, 1)) %>% 
  rename(Outcome = name) %>% 
  select(Outcome:Estimate, `95% CI`, `% Change`) %>% 
  kable("html", booktabs = T, col.names = c("Outcome","Pre","Post","Pre","Post","Unadjusted DID","Estimate","95% CI","% Change")) %>% 
  kable_styling(latex_options = c("striped")) %>%
  #pack_rows(index = c("Total Patients by Insurnace" = 4, "Quality Measure Components" = 6, "Financial Components" = 4)) %>% 
  add_header_above(c(" " = 1, "Control" = 2, "Treated" = 2, " " = 1, "Staggered DID" = 3))

@@

did2s(
      data = dfc.new %>% 
        inner_join(dfc %>% filter(Year == 2010 & ngla_net_gain_loss/ngla_revenue > 0.081 ) #& ngla_net_gain_loss/ngla_revenue < 0.03)  ngla_net_gain_loss/Assets < 0.05
                   %>% select(ID, Pct.NHA:Pct.COM) %>% unique() , by = c("ID")) , 
      yname = "Total", 
      treatment = "Tx",
        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.MCD + Pct.MCR + Pct.None, 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "ID",
      verbose = FALSE
    )

>>>>

df.profit <- df.profit %>% 
  left_join(dfc %>% filter(Year == 2010) %>% select(ID, ngla_net_gain_loss, ngla_revenue, ngla_expense, Assets, Pct.NHA:Pct.COM) %>% 
  mutate(pc = ngla_net_gain_loss / ngla_revenue) , by = c("ID")) %>% 
  filter(`BHCMIS ID` %notin% c("010450","0438280","070430"))

df.profit <- df.profit %>% 
  mutate(profit.class = ifelse(pc < 0.017, 1, 
              ifelse(pc >= 0.017 & pc <= 0.081, 2, 
              ifelse(pc > 0.081, 3, NA))))

splits1 <- c(min(df.profit$pc, na.rm = TRUE), splits)
splits2 <- c(splits, max(df.profit$pc, na.rm = TRUE))

@@

  df.temp <- df.profit[,c(1:9, j, 13:ncol(df.profit))] 
  colnames(df.temp)[10] <- "Outcome"
  outcomes <- did2s(
      data = df.temp %>% filter(pc >= splits1[g] & pc <= splits2[g]), 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.MCR + Pct.None, 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "ID",
      verbose = FALSE
    )

@@

data.frame(Subset = c(rep("Low", 3), rep("Medium", 3), rep("High", 3)),
      Outcome = rep(c("Total","Quality","Financial"), 3),
      Estimate = as.numeric(did.profit[,1]), 
      SD = as.numeric(did.profit[,2]))

@@

did2s(
      data = dfc.new %>% 
        inner_join(dfc %>% filter(Year == 2010 & ngla_net_gain_loss/ngla_revenue > 0.08 ) #& ngla_net_gain_loss/ngla_revenue < 0.03)  ngla_net_gain_loss/Assets < 0.05
                   %>% select(ID, Pct.NHA:Pct.COM) %>% unique() , by = c("ID")) , 
      yname = "Total", 
      treatment = "Tx",
        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.MCD + Pct.MCR + Pct.None, 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "ID",
      verbose = FALSE
    )
